### 2022-05-12 main/chapter_2ljets.tex
use epigraph; add hoare quote; se bibtex tidy

\chapterquote{Laws were made to be broken.}%
{Christopher North, 1785--1854}%: Blackwood's Magazine May 1830

@@

\clearpage

>>>>

\begin{epigraphs}
\qitem{%
An experiment is never a failure solely because it fails to
achieve predicted results. An experiment is a failure only when it also
fails adequately to test the hypothesis in question, when the data it
produces don’t prove anything one way or another.%
}%
{Robert M. Pirsig~\cite{pirsig1999zen}}
\qitem{%
But there is one feature I notice that is generally missing in cargo cult
science. \ldots\
% That is the idea that we all hope you have learned in studying science in
% school--we never say explicitly what this is, but just hope that you catch
% on by all the examples of scientific investigation. It is interesting,
% therefore, to bring it out now and speak of it explicitly.
It's a kind of scientific integrity, a principle of scientific thought that
corresponds to a kind of utter honesty --- a kind of leaning over backwards.%
}%
{Richard Feynman~\cite{feynman1974cargo}}
\end{epigraphs}
\clearpage

@@

### 2022-05-12 main/chapter_experiment.tex
use epigraph; add hoare quote; se bibtex tidy

\chapterquote{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future - would be interesting if NASA
made a telescope for that%
}%
{Ken M}

>>>>

\epigraph{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future --- would be interesting if NASA
made a telescope for that%
}%
{Ken M}

### 2022-05-12 main/chapter_searches.tex
use epigraph; add hoare quote; se bibtex tidy

\chapter{The ATLAS experiment}
\label{chapter:experiment}

\chapterquote{Laws were made to be broken.}%
{Christopher North, 1785--1854}%: Blackwood's Magazine May 1830

Hello

>>>>

\chapter{Searches in ATLAS}
\label{chapter:intro}

\epigraph{%
One way is to make it so simple that there are \emph{obviously} no deficiencies and the other way is to make it so complicated that there are
no \emph{obvious} deficiencies.%
}%
{Tony Hoare~\cite{hoare2007emperor}}

\section{Data analysis}

\section{Frequentist theory}

\epigraph{%
Within this theory, statistical methods of great practical usefulness have been
developed, and its statements can and frequently do contribute in a vague way
to the interpretation of data. \ldots%
}%
{John W. Pratt~\cite{pratt1961testing}}

\section{Post-frequentist practice}

\epigraph{%
\ldots\ But this book, by its very excellence, its thoroughness, lucidity and
precision, intensifies my growing feeling that nevertheless the theory is
arbitrary, be it however ``objective,'' and the problems it solves, however
precisely it may solve them, are not even simplified theoretical counterparts
of the real problems to which it is applied.%
}%
{John W. Pratt~\cite{pratt1961testing}}

\section{Searches}

### 2022-05-12 main/chapter_theory.tex
use epigraph; add hoare quote; se bibtex tidy

\chapterquote{%
The idea that theorems follow from the postulates does not correspond to simple
observation.
If the Pythagorean theorem were found to not follow from the postulates, we
would again search for a way to alter the postulates until it was true.
Euclid's postulates came from the Pythagorean theorem, not the other way.}%
{Richard Hamming~\cite{hamming1980unreasonable}}

\chapterquote{%
One geometry can not be more true than another; it can only be more convenient.
Geometry is not true, it is advantageous.}%
{Robert M. Pirsig~\cite{pirsig1999zen}}

>>>>

\begin{epigraphs}
\qitem{%
% The idea that theorems follow from the postulates does not correspond to simple
% observation.
%If the Pythagorean theorem were found to not follow from the postulates, we
%would again search for a way to alter the postulates until it was true.
Euclid's postulates came from the Pythagorean theorem, not the other way.}%
{Richard Hamming~\cite{hamming1980unreasonable}}
\qitem{%
One geometry can not be more true than another; it can only be more convenient.
Geometry is not true, it is advantageous.}%
{Robert M. Pirsig~\cite{pirsig1999zen}}
\end{epigraphs}

### 2022-05-12 main/frontmatter.tex
use epigraph; add hoare quote; se bibtex tidy

\begin{preface}
This thesis describes my research on various hoozywotsists.%
\footnote{test.}

@@

\pagequote{%
Begin reading at Chapter N.
Do \textbf{not} read the quotations that appear at the\\
beginning of the chapter.%
}%
{Donald E. Knuth~\cite{knuth1975art}}

>>>>

\begin{preface}
\epigraph{%
Begin reading at Chapter N. Do \emph{not} read the quotations
that appear at the beginning of the chapter.%
}%
{Donald E. Knuth~\cite{knuth1975art}}

This thesis describes my research on various hoozywotsists.%
\footnote{test.}

@@
